---
title: "Assemble a table of SNP pairs"
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(daeqtlr)
```

If your starting point for DAEQTL mapping is not the triad of the three data
objects introduced in `vignette('daeqtlr')` and you need to assemble the set of
SNP pairs for DAEQTL testing first, then this vignette is for you.

Here we show how to assemble a table of SNP pairs starting from:

- a list of DAE SNPs
- a list of candidate SNPs
- genomic positional annotation for those SNPs

Let us read in the three data sets above from the example files bundled with
this `{daeqtlr}`:

```{r}
dae_snps <- read_dae_snps(file = daeqtlr_example("dae_snps.txt"))
dae_snps[1:10, ]

candidate_snps <-
  read_candidate_snps(file = daeqtlr_example("candidate_snps.txt"))
candidate_snps[1:10, ]

snp_gen_positions <-
  read_snp_gen_positions(file = daeqtlr_example("snp_gen_positions.csv"))
snp_gen_positions[1:10, ]
```

We start by creating an intermediate data table (`snp_table`) with all the SNPs
involved and their genomic positions, as well as the indication of who is a DAE
SNP and who is a candidate SNP (they can be both). For that we use the function
`create_snp_table()`:

```{r}
snp_table <-
  create_snp_table(snp_gen_pos = snp_gen_positions,
                   dae_snps = dae_snps,
                   candidate_snps = candidate_snps)
snp_table
```

To create the set of SNP pairs, we use the function `create_snp_pairs()` that
takes in the `snp_table`. Essentially, the `create_snp_pairs()` searches within
a genomic neighborhood of each DAE SNP for other SNPs marked as candidate SNPs.
This genomic neighborhood is specified via a genomic window size centered on
the DAE SNP. The window size defaults to 500 kb (`window_size = 500000L`),
meaning a total of 1 Mb around the DAE SNP's position (500 kb to each side). 

```{r}
# Assembles a data table of SNP pairs
snp_pairs <- create_snp_pairs(snp_table = snp_table)

snp_pairs
```

And there you have it, the SNP pairs needed for DAEQTL mapping as explained in
`vignette('daeqtlr')`.
